Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems

### 2024-06-19 final/oup-authoring-template.tex
Add EBML funding

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions.
This work was supported in part by funds from
the Agencia I+D+i (PICT-2018-01516),
and Universidad de Buenos Aires (UBAINT Doctoral, REREC-2023-593-E-UBA-REC).

>>>>

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions.
This work was supported in part by funds from
the Agencia I+D+i (PICT-2018-01516),
Universidad de Buenos Aires (UBAINT Doctoral, REREC-2023-593-E-UBA-REC),
and EMBL core funding.
